\textbf{Using the MSU Thesis Class}

### 2011-09-20 msu-thesis.tex
2.1 documentation update

\documentclass[11pt]{article}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics and Languages\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version 2.0\\August 25, 2011}
\usepackage[T1]{fontenc}
\usepackage[margin=1.25in]{geometry}
\usepackage{titling}
\usepackage[utf8]{inputenc}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf]{titlesec}
\usepackage[colorlinks=true]{hyperref}

@@

\section{Bugs and redistribution}
\subsection{Current version}
The latest copy of \pkg{msu-thesis} will always be available here \url{http://www.msu.edu/~amunn/latex/msu-thesis.zip} and on  \href{http://tug.ctan.org/cgi-bin/ctanPackageInformation.py?id=msu-thesis}{CTAN}. If you use TeXLive, then \pkg{tlmgr} will update or install the latest version. If you want others to use the class, \textsc{please} point them to those links, so that they can get an up-to-date version with all accompanying documentation and examples rather than passing along your copy. Please report \textsc{any} problems you have with the class to me \href{mailto:amunn@msu.edu}{amunn@msu.edu}, as this will aid in making things easier for those who follow you.
\subsection{Version history}
Previous versions of \pkg{msuthesis} (versions 1.0--1.4b) were created for non-electronic submission and should not be used. Versions 1.5--1.6 (the first electronic submission versions) contained a |\makeabstract| command and a separate |msuabstract| environment. These have been removed as of version 1.7.  Users who are upgrading from earlier versions to version 1.7 do not need to change these commands however but their use will trigger a warning.)
\section{Acknowledgements}
Thanks to Lars Masden, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0-1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex} spacing fix code, and Leo Liu for the landscape page numbering code, which greatly simplified my original version. Thanks also to Matt Husband, Irina Agafonova, and Dmitriy Bryndin for reporting problems during initial testing.

>>>>

\documentclass[11pt]{article}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics and Languages\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version 2.1\\September 20, 2011}
\usepackage[T1]{fontenc}
\usepackage[margin=1.25in]{geometry}
\usepackage{titling}
\usepackage[utf8]{inputenc}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf]{titlesec}
\usepackage[colorlinks=true]{hyperref}

@@

\section{Bugs and redistribution}
\subsection{Current version}
The latest copy of \pkg{msu-thesis} will always be available here \url{http://www.msu.edu/~amunn/latex/msu-thesis.zip} and on  \href{http://tug.ctan.org/cgi-bin/ctanPackageInformation.py?id=msu-thesis}{CTAN}. If you use TeXLive, then \pkg{tlmgr} will update or install the latest version. If you want others to use the class, \textsc{please} point them to those links, so that they can get an up-to-date version with all accompanying documentation and examples rather than passing along your copy. Please report \textsc{any} problems you have with the class to me \href{mailto:amunn@msu.edu}{amunn@msu.edu}, as this will aid in making things easier for those who follow you.
\subsection{Version history}
Previous versions of \pkg{msuthesis} (versions 1.0--1.4b) were created for non-electronic submission and should not be used. Versions 1.5--1.6 (the first electronic submission versions) contained a |\makeabstract| command and a separate |msuabstract| environment. These have been removed as of version 1.7.  Users who are upgrading from earlier versions to version 1.7 do not need to change these commands however but their use will trigger a warning.)
\section{Acknowledgements}
Thanks to Lars Masden, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0-1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex} spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version, and Florent Chervet for the hyperref code. Thanks also to Matt Husband, Irina Agafonova, and Dmitriy Bryndin for reporting problems during initial testing.
